Ms 1

### 2017-05-29 ms1/ms1_display.Rmd
cohort, updates

x %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>%
  kable

x %>% ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~ antibiotic, ncol=3, scales='free_y') +
  geom_point() + geom_line() +
  theme_minimal()
```

>>>>

x %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>%
  kable
```

```{r}
x %>% ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~ antibiotic, ncol=3, scales='free_y') +
  geom_point() + geom_line() +
  theme_minimal()
ggsave('~/tmp.pdf')
```
